---
engine: knitr
---

```{r datalocation}
#| include: false
#| error: true

library(tidyverse)
library(jsonlite)

meta <- read_json("meta.json")
meta_uns <- meta$uns

filesize <- format(structure(meta_uns$file_size, class="object_size"), units="auto", standard="IEC", digits=2)

n_cells<- NULL

for (item in meta$structure$var) {
  if (item$name == "n_cells") {
    n_cells <- item$shape[[1]]
    break
  }
}

```

 
---
title: "`r meta_uns$dataset_id`"
subtitle: "`r meta_uns$dataset_summary`"
description: |
  `r meta_uns$dataset_description`
  [Documentation](`r meta_uns$dataset_url`) [Download](`r meta_uns$data_url`)
title-block-banner-color: white
categories: 
  - Openproblems v1
  - public
  - theis
css: ../../../events/events.css
toc: false
listing:
  - id: benchmarks
    contents: "../../../results/*/index.qmd"
    type: table
---

created on `r meta_uns$date_created`


Dataset size: `r filesize`

number of cells: `r n_cells`

### Explore the dataset

::: {.panel-tabset}

## X
```{r x_struct}
#| echo: false

structure <- meta$structure

x_df <- fromJSON(toJSON(structure$X))

x_df

```

## layers

```{r layers_struct}
#| echo: false

layers_df <- fromJSON(toJSON(structure$layers))

layers_df

```

## obs

```{r obs_struct}
#| echo: false

obs_df <- fromJSON(toJSON(structure$obs))

obs_df %>% 
  select(name, type, shape, dtype)

```

:::



#### Related Benchmarks

::: {.benchmarks}
:::
