---
title: Define the task
order: 10
engine: knitr
---


{{< include /_include/_clone_repo.qmd >}}
{{< include /_include/_evaluate_code.qmd >}}
{{< include /_include/_read_api.qmd >}}

Before writing any code, it's essential to carefully plan and document your task to ensure its relevance, feasibility, and compatibility with the OpenProblems framework. 

## Step 1: Check whether a similar task already exists

Please check the [OpenProblems tasks](https://github.com/openproblems-bio/openproblems-v2/issues?q=label%3Atask+) to see whether a similar task has already been created.

## Step 2: Create a GitHub issue

If not, [create a new issue](https://github.com/openproblems-bio/openproblems-v2/issues/new?assignees=&labels=task&projects=&template=new_task.yml) and fill in the required information.

This collaborative process will help ensure that your task is well-defined, relevant, and compatible with the OpenProblems framework. Additionally, it informs others of your ongoing work in this area and establishes a foundation for potential collaboration. Check out [some examples](https://github.com/openproblems-bio/openproblems-v2/labels/task) by filtering on the 'task' label on GitHub.

```{r echo=FALSE, warning=FALSE, error=FALSE}
new_task_yml <- yaml::read_yaml(".github/ISSUE_TEMPLATE/new_task.yml")
md <- paste(sapply(new_task_yml$body, function(section) {
  if (section$type == "textarea") {
    paste0("### ", section$attributes$label, "\n\n", section$attributes$description, "\n")
  } else {
    ""
  }
}), collapse = "\n")

knitr::asis_output(md)
```

## Step 3: Create task info

Now create a task info metadata file in the `src/tasks/<task_id>/api` directory. This file will be part of the automatic "readme" creation in the repo directory of this task. The task info file should be named `task_info.yaml` and should contain the following information:


```{r echo=FALSE, warning=TRUE, error=TRUE}
info <- read_and_merge_yaml("src/common/schemas/task_info.yaml")

process <- function(info, prefix = "", required = NA) {

    prop_names <-
      names(info$properties)
    req_prop <-
      info$required

    unlist(lapply(
      prop_names,
      function(prop_name) {
        prop <- info$properties[[prop_name]]
        process(prop, prefix = paste0(prefix, ".", prop_name), required = required)
      }
    ))
  # } else if (type == "array") {
  #   c() # ignore for now
  # } else if (is.list(info)) {
  #   paste0(
  #     prefix, "`\n",
  #     "\n",
  #     info$description
  #   )
  # } else {
  #   c()
  # }
}
info_str <- paste(process(info, required = TRUE), collapse = "\n\n")

knitr::asis_output(info_str)
```




<!-- ```{.yaml filename="src/tasks/<task_id>/api/task_info.yaml"}
task_id: your_task_id # <1>
task_name: Your task name # <2>
summary: "FILL IN: A one line description of what this purpose of this task is." # <3>
description: | # <4>
  FILL IN: The task description and motivation you created earlier. # <4>
authors: # <5>
  - name: "Your name" # <5>
    roles: [ author, maintainer ] # <5>
    info: # <5>
      github: your-github-account # <5>
      orcid: "0000-1111-2222-3333" # <5>
``` -->
1. Provide the task id in snakecase format e.g. label_projection (no spaces, no special characters, only lowercase letters and underscores).
2. Provide the full task name in normal formatted text e.g. Label Projection (can contain spaces and special characters).
3. Provide a one line description of what the purpose of the task is.
4. Provide the task description and motivation from the previous created github issue.
5. Provide all authors who helped create the task. You can add more authors by adding more `- name: ...` entries. The `roles` field can be used to specify the role of the author. The `info` field can be used to specify additional information about the author. For more information about the `roles` and `info` fields see the [viash documentation](https://viash.io/reference/config/functionality/author.html).



## Next steps

You are now well-equipped to begin [designing the API](design_api.qmd) for the new benchmarking task.