---
title: Add a dataset
order: 30
engine: knitr
---

{{< include ../../_include/_clone_repo.qmd >}}
{{< include /_include/_evaluate_code.qmd >}}
{{< include /_include/_synchonize_tabs.qmd >}}

Datasets are required for any benchmarking workflow and need to be preprocessed in a standardized way.
The `datasets` task provides a framework for loading and preprocessing datasets.

This guide will show you how to create a new [Viash](https://viash.io) component.
In the following we will show examples for both Python and R.

:::{.callout-tip}
Make sure you have followed the ["Getting started"](../fundamentals/getting_started.qmd) guide.
:::

## OpenProblems datasets

Common datasets are created by generating raw datasets with a data loader and running them through the pre-processing pipeline (@fig-dataflow). Afterwards, further task-specific processing occurs prior to the task-specific benchmarking workflow.

{{< include ../_figures/_project_structure_dataflow.qmd >}}

See the [reference documentation](../reference/openproblems-v2/src-datasets.qmd) for more information on how each of these steps works.

```{r setup-packages, include=FALSE}
library(tidyverse)
library(rlang)
```


## Step 1: Create a directory for the dataset loader

To add a dataset to OpenProblems, you will need to create a Viash component for a dataset loader. 

```{r, include=FALSE, eval=TRUE}
# set eval to TRUE to make sure is always run, even when profile is not 'evaluate_code'
dir <- "src/datasets/loaders/myloader"
if (!dir.exists(dir)) {
  dir.create(dir)
}
```
```{bash, eval=FALSE}
mkdir src/datasets/loaders/myloader
```

:::{.callout-tip}
Take a look at the dataset loaders that are already in the `src/datasets/loaders`! Likely there is already a dataset loader that already does something similar to what you need.
:::

## Step 2: Create a Viash config

Next, create a config for the dataset loader.
The [Viash config](https://viash.io/reference/config/) contains metadata of your dataset, which script is used to run it, and the required dependencies. 
The simplest dataset loader you can create looks as follows.

```{bash, include=FALSE, eval=TRUE}
# set eval to TRUE to make sure is always run, even when profile is not 'evaluate_code'
cat > src/datasets/loaders/myloader/config.vsh.yaml << 'HERE'
functionality:
  name: "myloader"
  namespace: "datasets/loaders"
  description: "A new dataset loader"
  arguments:
    - name: "--output"
      __merge__: ../../api/anndata_raw.yaml
      direction: "output"
  resources:
    - type: python_script
      path: script.py
platforms:
  - type: docker
    image: python:3.10
    setup:
      - type: python
        pypi: anndata~=0.8.0
  - type: nextflow
HERE
```

:::{.panel-tabset}

## Python

Contents of `src/datasets/loaders/myloader/config.vsh.yaml`:

```{embed, lang="yaml"}
src/datasets/loaders/myloader/config.vsh.yaml
```

## R

Contents of `src/datasets/loaders/myloader/config.vsh.yaml`:

```yaml
functionality:
  name: "myloader"
  namespace: "datasets/loaders"
  description: "A new dataset loader"
  arguments:
    - name: "--output"
      __merge__: ../../api/anndata_raw.yaml
      direction: "output"
  resources:
    - type: python_script
      path: script.py
platforms:
  - type: docker
    image: eddelbuettel/r2u:22.04
    setup:
      - type: r
        cran: anndata
      - type: apt
        packages: [ libhdf5-dev, libgeos-dev, python3, python3-pip, python3-dev, python-is-python3 ]
  - type: nextflow
```
:::

For more parameter options, refer to ["Parameters"](#parameters) section.


## Step 3: Create a script

Next, create a script that will generate or load the dataset.
Here we show an example script that generates a random dataset, but check out `src/datasets/loaders` for real data examples.
The script must ensure that that the output anndata object has the format as described in the ["Format of a raw dataset object"](#format-of-a-raw-dataset-object-format) section.


```{bash, include=FALSE, eval=TRUE}
# set eval to TRUE to make sure is always run, even when profile is not 'evaluate_code'
cat > src/datasets/loaders/myloader/script.py << 'HERE'
import anndata as ad
import pandas as pd
import scipy
import numpy as np
import random

## VIASH START
par = {"output": "output.h5ad"}
## VIASH END

# Create obs data for the cells
obs = pd.DataFrame({
    "celltype": random.choices(["enterocyte", "intestine goblet cell", "stem cell"], k=100),
    "batch": random.choices(["experiment1", "experiment2"], k=100),
    "tissue": random.choices(["colon", "ileum"], k=100)
})

# Create var data for the genes
var = pd.DataFrame(
    index=["APP", "AXL", "ADA", "AMH"]
)

# Create counts data
counts = scipy.sparse.csr_matrix(
  np.random.poisson(0.3, (obs.shape[0], var.shape[0]))
)

# Create an AnnData dataset
adata = ad.AnnData(
  layers = {
    "counts": counts
  },
  obs = obs,
  var = var,
  uns = {
    "dataset_id": "my_dataset",
    "dataset_name": "My dataset",
    "data_url": "https://url.to/dataset/source",
    "data_reference": "mydatasetbibtexreference",
    "dataset_summary": "A short description of the dataset.",
    "dataset_description": "Long description of the dataset.",
    "dataset_organism": "homo_sapiens"
  }
)

# Write to file
adata.write_h5ad(par["output"], compression="gzip")
HERE
```

:::{.panel-tabset}

## Python

Contents of `src/datasets/loaders/myloader/script.py`:

```{embed, lang="python"}
src/datasets/loaders/myloader/script.py
```

## R

Contents of `src/datasets/loaders/myloader/script.R`:

```r
library(anndata)
library(Matrix)
library(dplyr)

## VIASH START
par <- list("output" = "output.h5ad")
## VIASH END

# Create obs data for the cells
obs <- data.frame(
  "celltype" = sample(c("enterocyte", "intestine goblet cell", "stem cell"), 100, replace = TRUE),
  "batch" = sample(c("experiment1", "experiment2"), 100, replace = TRUE),
  "tissue" = sample(c("colon", "ileum"), 100, replace = TRUE)
)

# Create var data for the genes
var <- data.frame(
  row.names = c("APP", "AXL", "ADA", "AMH")
)

# Create counts data
counts <- Matrix::rsparsematrix(
  nrow(obs), 
  nrow(var),
  density = 0.3,
  rand.x = function(n) rpois(n, 100)
)

# Create an AnnData dataset
adata <- AnnData(
  layers = list(
    "counts" = counts
  ),
  obs = obs,
  var = var,
  uns = list(
    dataset_id = "my_dataset",
    dataset_name = "My dataset",
    data_url = "https://url.to/dataset/source",
    data_reference = "mydatasetbibtexreference",
    dataset_summary = "A short description of the dataset.",
    dataset_description = "Long description of the dataset.",
    dataset_organism = "homo_sapiens"
  )
)

# Write to file
adata$write_h5ad(par[["output"]], compression = "gzip")
```

:::

## Step 4: Run the component

Try running your component! You can start off by running your script inside your IDE.

To check whether your component works as a standalone component, run the following commands.

(Re)build the Docker container after changing the `platforms` section in the Viash config:
```bash
viash run src/datasets/loaders/myloader/config.vsh.yaml -- \
  ---setup cachedbuild
```

Run the component:
```bash
viash run src/datasets/loaders/myloader/config.vsh.yaml -- \
  --output mydataset.h5ad
```

<!-- TODO: write a generic dataset loader unit test and use that instead, see #103 -->

## Parameters

It's possible to add arguments to the dataset loader by adding additional entries to the `functionality.arguments` section in the `config.vsh.yaml`. For example:

```yaml
arguments:
  - name: "--n_obs"
    type: "integer"
    description: "Number of cells to generate."
    default: 100
  - name: "--n_vars"
    type: "integer"
    description: "Number of genes to generate."
    default: 100
```

You can then use the `n_obs` and `n_vars` values in the `par` object to get access to the runtime parameters:

:::{.panel-tabset}

## Python

```python
obs = pd.DataFrame({
    "celltype": random.choices(["enterocyte", "intestine goblet cell", "stem cell"], k=par["n_obs"]),
    "batch": random.choices(["experiment1", "experiment2"], k=par["n_obs"]),
    "tissue": random.choices(["colon", "ileum"], k=par["n_obs"])
})
var = pd.DataFrame(
    index=[f"Gene_{i}" for i in range(100)]
)
```

## R

```r
obs <- data.frame(
  "celltype" = sample(c("enterocyte", "intestine goblet cell", "stem cell"), par$n_obs, replace = TRUE),
  "batch" = sample(c("experiment1", "experiment2"), par$n_obs, replace = TRUE),
  "tissue" = sample(c("colon", "ileum"), par$n_obs, replace = TRUE)
)
var <- data.frame(
  row.names = paste0("Gene_", seq_len(par$n_vars))
)
```

:::

## Format of a raw dataset object

```{r, include=FALSE}
yaml_file <- "src/datasets/api/anndata_raw.yaml"
spec_anndata_raw <- yaml::read_yaml(yaml_file)
arg <- spec_anndata_raw

slots <- map2_df(
  names(arg$info$slots), 
  arg$info$slots, 
  function(group_name, slot) {
    df <- map_df(slot, as.data.frame)
    df$struct <- group_name
    df$file_name <- basename(yaml_file) %>% gsub("\\.yaml", "", .)
    df$multiple <- df$multiple %||% FALSE %|% FALSE
    as_tibble(df)
  }
)

example <- slots %>%
  group_by(struct) %>%
  summarise(
    str = paste0(unique(struct), ": ", paste0("'", name, "'", collapse = ", "))
  ) %>%
  arrange(match(struct, c("obs", "var", "uns", "obsm", "obsp", "varm", "varp", "layers")))

example_str <- c("    AnnData object", paste0("     ", example$str))
```

Ideally, the AnnData output object should at least contain the following slots:

```{r, echo=FALSE, output="asis"}
cat(paste0(example_str, "\n"))
```

The full file format spec of a raw dataset AnnData is shown in the table below.

:::{.column-body-outset}
```{r, echo=FALSE}
slots %>%
  transmute(
    Struct = struct,
    Name = name,
    Type = type,
    Required = ifelse(required, "yes", ""),
    Description = description
  ) %>%
  knitr::kable()
```
:::

## Next steps

If your component works, please [create a pull request](../create_component/create_pull_request.qmd). After your dataset loader has been merged into the main branch, it will be used to generate a common dataset. After the common datasets have been generated, it will be picked up by the task-specific dataset processors if it has all of the slots required by the task.